
### Title: CUNY SPS MDS Data607_Assignment2"
### Author: Charles Ugiagbe
### Date: "9/3/2021"



### Introduction
##### This assignment demonstrates ability to connect to a SQL database from R

#### Load the required libraries


```{r}
library(RODBC)
library(tidyverse)
```

### Connect to the MySQL database using odbc connect and a dsn
```{r}
conn <- odbcConnect("MySQL_dsn")
```

#### Read files
Read the reviewers information from MySQL database into R 
```{r}
sqlQuery(conn, "Select * FROM Review limit 15")
```

Read the Dataframe into R
```{r}
query <- "Select * from Review"
df <- sqlQuery(conn, query)
```

check the head to have an idea of the data
```{r}
head(df)
```


#### Structure
##### Check the Structure of the data
```{r}
str(df)
```

Check the dataframe when review is "3"
```{r}
sqlQuery(conn, "Select * FROM Review where rating = 3")
```

#### Check if the dataframe contains any missing values
```{r}
anyNA.data.frame(df)
```
```{r}
anyNA.data.frame(df$Rating)
```







